The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-07 full_paper_draft.Rmd
fixing regression tables

export_summary_table(dfSummary(flood_total))

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valleys = case_when(dept %in% c("Chuquisaca", "Cochahamba", "Tarija") ~ 1, TRUE ~ 0),
         mountains = case_when(dept %in% c("La Paz", "Oruro", "Potosi") ~ 1, TRUE ~ 0),
         plains = case_when(dept %in% c("Beni", "Pando", "Santa Cruz") ~ 1, TRUE ~ 0),
         flood_secondary = floods * secondary,
         drought_secondary = droughts * secondary,
         flood_pov = floods * extr,
         drought_pov = droughts * extr,
         flood_lny = floods * lny,
         drought_lny = floods * lny,
         lag_flood_lny = lag_floods * lny,
         lag_drought_lny = lag_droughts * lny,
         lag_f_secondary = lag_floods * secondary,
         lag_d_secondary = lag_droughts * secondary)

@@

#creating rural sample
rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary"))

@@

urban <- subset(reg_data, rural == 0, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary"))

@@

```{r generate probit regression table region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_g, probitMod_register_g, probitMod_work_g), 
               title = "Full sample probit regression results", 
               label = "fullResults13",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

```{r generate probit regression table rural sample region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_rg, probitMod_register_rg, probitMod_work_rg), 
               title = "Rural sample probit regression results", 
               label = "fullResults14",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

```{r generate probit regression table urban sample region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_ug, probitMod_register_ug, probitMod_work_ug), 
               title = "Urban sample probit regression results", 
               label = "fullResults15",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

model_assist_r <- (lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_assist_r)
model_register_r <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)
summary(model_register_r)
model_reason_r <- (lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))
summary(model_reason)

@@

The "assist" variable shows that around 60% of people who are registered for school currently assist, while 40% do not assist. The "reason" variable shows that two most common reasons for missing school are for work (31.3%) or vacation (20.5). Out of the people who are registered for school, 6.6% are repeating the grade they are currently in.

>>>>

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         dept_factor = as.factor(dept),
         lny = log(income + 1),
         valleys = case_when(dept %in% c("Chuquisaca", "Cochahamba", "Tarija") ~ 1, TRUE ~ 0),
         mountains = case_when(dept %in% c("La Paz", "Oruro", "Potosi") ~ 1, TRUE ~ 0),
         plains = case_when(dept %in% c("Beni", "Pando", "Santa Cruz") ~ 1, TRUE ~ 0),
         flood_secondary = floods * secondary,
         drought_secondary = droughts * secondary,
         flood_pov = floods * extr,
         drought_pov = droughts * extr,
         flood_lny = floods * lny,
         drought_lny = droughts * lny,
         lag_flood_lny = lag_floods * lny,
         lag_drought_lny = lag_droughts * lny,
         lag_f_secondary = lag_floods * secondary,
         lag_d_secondary = lag_droughts * secondary)

@@

#creating rural sample
rural <- subset(reg_data, rural == 1, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary", "lag_floods", "lag_droughts"))

@@

urban <- subset(reg_data, rural == 0, select = c("hh_id", "id", "age", "female", "literacy", "dept_factor", "rural", "lny", "attend", "register", "floods", "droughts", "year", "child", "grandchild", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor", "work_reason", "secondary", "valleys", "mountains", "plains", "dept", "extr", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov", "flood_lny", "drought_lny", "lag_flood_lny", "lag_drought_lny", "lag_f_secondary", "lag_d_secondary", "lag_floods", "lag_droughts"))

@@

```{r generate probit regression table region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_g, probitMod_register_g, probitMod_work_g), 
               title = "Full sample probit regression results (region fixed-effects)", 
               label = "fullResults13",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

```{r generate probit regression table rural sample region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_rg, probitMod_register_rg, probitMod_work_rg), 
               title = "Rural sample probit regression results (region fixed-effects)", 
               label = "fullResults14",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

```{r generate probit regression table urban sample region, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_ug, probitMod_register_ug, probitMod_work_ug), 
               title = "Urban sample probit regression results (region fixed-effects)", 
               label = "fullResults15",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_lny", "drought_lny","age", "female", "lny", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead", "mountains", "plains"))

@@

model_assist_r <- (lm(attend ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))

model_register_r <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)

model_reason_r <- (lm(work_reason ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural))

@@
